Supplemental Appendix for ``An asymptotically normal out-of-sample test of equal predictive accuracy for nested models''

### 2015-01-07 appendix.tex
Several minor edits and corrections

\noindent%
This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test of equal
predictive accuracy for nested models.''  Define the following
additional terms:
\begin{equation*}
  F_t(\beta) = (4 x_t'\beta - 2 y_{t+1} - 2 \yh_{t+1}) x_t',
\end{equation*}
$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
$H_t = \sum_{s=1}^{t-1} x_t \ep_{t+1} / (t-1)$.
And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.

@@

  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
  that~\eqref{eq:4} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
  \end{gather}
  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big) (2 x_t'\btrue - y_{t+1} - \yh_{t+1}) \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
\end{proof}

@@

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t' \big\rVert
    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

@@

This Lemma establishes that \citepos{Wes:96} basic results hold under
our weaker moment and dependence conditions and provides several
extensions. To streamline the presentation, we'll assume in these
proofs that $x_t$ is a scalar.
\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
    of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
    constants and coefficients. Note that $t^{a-1} x_t \ep_{t+1}$ is
    also an $L_2$-mixingale array with constants $t^{a-1} c_s$ and
    coefficients $\zeta_k$, since
    \begin{align*}
      \| \E_{t-k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \| \E_{t-k} x_t \ep_{t+1} \| \\
      &\leq (t^{a-1} c_t) \zeta_k
    \end{align*}
    and
    \begin{align*}
      \| x_t \ep_{t+1} t^{a-1} - \E_{t+k} x_t \ep_{t+1} t^{a-1} \| &= t^{a-1} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
      &\leq (t^{a-1} c_t) \zeta_{k+1}.
    \end{align*}

    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
    \begin{align*}
      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta/2} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2a - 2 + \delta}
    \end{align*}
    where the second inequality follows from \citepos{Mcl:75} maximal
    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
    Corollary 16.10). The summation converges to a constant as $T \to
    \infty$ and $(R'-1)^{-\delta} \to 0$, completing the proof.

  \item As in Part 1, $x_t \ep_{t+1} t^{a-1}$ is an $L_2$-mixingale of size
    $-1/2$ and we can use \citepos{Mcl:75} maximal inequality to get
    \begin{align*}
      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
    \end{align*}
    which again converges to a finite limit.
  \item The same argument used in Part 1 implies that $\omaxb{t} |
    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
    the result follows.
  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
  \item We have
    \begin{align*}
      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      &\leq \omaxb{t} |\hat{B}_t - B|
      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
    \end{align*}
    and both terms converge to zero in probability by Parts 1 and 3.
  \item Similar to the previous argument, we have
    \begin{align*}
      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
    \end{align*}
    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
  \end{enumerate}
\end{proof}

>>>>

\noindent%
This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test of equal
predictive accuracy for nested models.''  Define the following
additional terms:
\begin{equation*}
  F_t(\beta) = 2 (x_t'\beta - \yh_{t+1}) x_t',
\end{equation*}
$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
$H_t = \sum_{s=1}^{t-1} x_t \ep_{t+1} / (t-1)$.
And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.

@@

  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
  that~\eqref{eq:4} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
  \end{gather}
  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero in probability by construction. The proof of~\eqref{eq:5} is similar.
\end{proof}

@@

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

@@

This Lemma establishes that \citepos{Wes:96} basic results hold under
our weaker moment and dependence conditions and provides several
extensions. To streamline the presentation, we'll assume in these
proofs that $x_t$ is a scalar.
\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
    of size $-1/2$; let $c_t$ and $\zeta_k$ denote its mixingale
    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
    coefficients $\zeta_k$, since
    \begin{align*}
      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_k
    \end{align*}
    and
    \begin{align*}
      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_{k+1}.
    \end{align*}

    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
    \begin{align*}
      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
    \end{align*}
    where the second inequality follows from \citepos{Mcl:75} maximal
    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
    Corollary 16.10). The summation converges to a constant as $T \to
    \infty$ and $(R'-1)^{-2\delta} \to 0$, completing the proof.

  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
    \begin{align*}
      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
    \end{align*}
    which converges to a finite limit.
  \item The same argument used in Part 1 implies that $\omaxb{t} |
    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
    the result follows.
  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
  \item We have
    \begin{align*}
      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      &\leq \omaxb{t} |\hat{B}_t - B|
      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
    \end{align*}
    and both terms converge to zero in probability by Parts 1 and 3.
  \item Similar to the previous argument, we have
    \begin{align*}
      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
    \end{align*}
    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
  \end{enumerate}
\end{proof}
